Instructions for ACL 2020 Proceedings

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Few typos

\begin{document}
\maketitle
\begin{abstract}
  Basically we want to see if language models pre-trained on text data are useful for dialogue.
  So we look at if BERT is useful for dialouge act recoginiton.
  But we want to know if it's really adapting to the domain, so we look at how it uses laughter, a phenomenon specific to dialogue.
\end{abstract}

@@

\begin{table}
  \label{tab:laughter}
  \centering
  \begin{tabular}{@{}lccc@{}}
    \toprule
    & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
    Forward-CF & 11.86 & 4.59 & 11.40\\
    Backward-CF & 11.57 & 3.03 & 4.30\\
    Other & 12.71 & 4.40 & 2.39\\
    CS & 20.63 & 14.17 & -1.50\\\bottomrule

  \end{tabular}
  \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
\end{table}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Basically we want to see if language models pre-trained on text data are useful for dialogue.
  So we look at if BERT is useful for dialogue act recognition.
  But we want to know if it's really adapting to the domain, so we look at how it uses laughter, a phenomenon specific to dialogue.
\end{abstract}

@@

% \begin{table}
%   \label{tab:laughter}
%   \centering
%   \begin{tabular}{@{}lccc@{}}
%     \toprule
%     & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
%     Forward-CF & 11.86 & 4.59 & 11.40\\
%     Backward-CF & 11.57 & 3.03 & 4.30\\
%     Other & 12.71 & 4.40 & 2.39\\
%     CS & 20.63 & 14.17 & -1.50\\\bottomrule

%   \end{tabular}
%   \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
% \end{table}
